\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage[hyphens]{url}
\usepackage{microtype}
\usepackage{parskip}

\begin{document}
\thispagestyle{empty}

\today

\vspace{0.8em}

\noindent The Editor-in-Chief\\
\textit{Journal of Imaging}, MDPI

\vspace{0.8em}

\noindent Dear Editor,

\vspace{0.5em}

We respectfully submit our manuscript, \textbf{``HypEReg-TransMorph: A Hyperelastic-Regularized Transformer Framework for Folding-Suppressed Deformable Brain MRI Registration''}, for consideration as an original research article in the \textit{Journal of Imaging}.

\vspace{0.5em}
\noindent\textbf{Clinical motivation and significance.}
Accurate deformable brain MRI registration underpins a wide range of clinical neuroimaging workflows---from atlas-based segmentation and radiotherapy organ-at-risk delineation, to tensor-based morphometry (TBM) endpoints used in Alzheimer's disease progression monitoring, multiple sclerosis lesion analysis, and pre-surgical planning for deep brain stimulation and epilepsy resection. A fundamental but often overlooked requirement of all these applications is that the estimated deformation field must be \emph{diffeomorphic}: local foldings (voxels where the Jacobian determinant $\det J_\phi \le 0$) corrupt Jacobian-based biomarkers, produce anatomically inconsistent label boundaries, and force time-consuming manual post-correction. Contemporary Transformer-based registration methods have achieved state-of-the-art overlap accuracy, yet they routinely produce folded deformation fields that violate the assumptions of downstream clinical analysis pipelines. This practical gap---high overlap accuracy at the cost of physically implausible deformations---is the precise problem our work addresses.

\vspace{0.5em}
\noindent\textbf{Technical contribution and key results.}
We introduce \textbf{HypEReg}, a compact, differentiable, plug-in regularizer derived from hyperelastic energy principles (a volume-distortion penalty combined with an explicit anti-folding hinge) and integrate it as a training-time loss term into the TransMorph backbone. Because HypEReg modifies only the loss function and leaves the inference architecture unchanged, it incurs \emph{zero additional inference overhead} (measured forward runtime: 0.43\,s/volume; peak memory: 5.42\,GB---identical to the unregularized TransMorph baseline).

On the IXI atlas-to-subject benchmark evaluated over \textbf{115 held-out test subjects} with full paired Wilcoxon/BH-FDR inferential statistics, HypEReg-TransMorph achieves the following improvements over strong Transformer baselines:

\begin{center}
\renewcommand{\arraystretch}{1.25}
\begin{tabular}{lccc}
\hline
\textbf{Metric} & \textbf{HypEReg-TransMorph} & \textbf{TransMorph} & \textbf{TransMorphBayes}\\
\hline
Dice ($\uparrow$) & \textbf{0.7537} & 0.7527 & 0.7530\\
Non-pos.\ $\det J_\phi$ ratio ($\downarrow$) & \textbf{1.5\,$\times$\,10$^{-5}$} & 0.0150 & 0.0156\\
SDlogJ ($\downarrow$) & \textbf{0.328} & 0.506 & 0.492\\
HD95 mm ($\downarrow$) & \textbf{3.16} & 5.88 & 3.37\\
ASSD mm ($\downarrow$) & \textbf{0.589} & 1.559 & 0.622\\
\hline
\end{tabular}
\end{center}

\noindent The non-positive Jacobian determinant ratio---the direct measure of deformation field validity for clinical use---is reduced by a factor of \textbf{$>$1,000$\times$} relative to the unregularized TransMorph baseline ($p < 10^{-19}$, $q < 10^{-19}$, rank-biserial effect $= 1.00$), while grouped-VOI Dice is simultaneously improved. These results demonstrate, for the first time on this benchmark, that Jacobian-aware regularization can deliver near-diffeomorphic Transformer-based registration without any sacrifice in alignment fidelity or inference speed---directly addressing the clinical usability barrier noted above.

\vspace{0.5em}
\noindent\textbf{Suitability for \textit{Journal of Imaging}.}
We believe this work fits squarely within the journal's scope: it presents a principled, reproducible methodological contribution to medical image analysis with direct translational relevance to clinical neuroimaging. A complete reproducibility package (training code, evaluation scripts, per-case metric tables, figure pipelines, and model checkpoints available upon request) is released openly at \url{https://github.com/Zzxmh/HypEReg-TransMorph} and archived at Zenodo (DOI: 10.5281/zenodo.19888526).

\vspace{0.5em}
\noindent\textbf{Declarations.}
This manuscript has not been published or submitted elsewhere; all authors have approved this submission; the authors declare no conflicts of interest; no external funding was received for this work.

\vspace{1em}

\noindent Sincerely,\\[0.5em]
\noindent Shiyi Xu (first author)\\
Capital Medical University, Beijing 100069, China\\
\texttt{xsy4831@mail.ccmu.edu.cn}

\vspace{0.5em}
\noindent Mohan Xu (corresponding author)\\
School of Physics, Peking University, Beijing 100871, China\\
\texttt{2200011601@stu.pku.edu.cn}

\end{document}
